Detecting Hate Speech with GPT-3

### 2022-03-18 outputs/documents/paper.Rmd
Data collection for multiple iterations of few-shot single catgory, updates to tables in paper, begin updates to results sections

We examine the ability of GPT-3 to identify hate speech in zero-shot, one-shot, and few-shot settings. There are a variety of parameters, such as temperature, that control the degree of text variation. Temperature is a hyper-parameter between zero and one. Lower temperatures mean that the model places more weight on higher-probability tokens. To enhance consistency, the temperature is set to zero in our experiments and not varied. There are two categories of hate speech that are of interest in this paper. The first targets the race of the recipient, and the other targets the gender of the recipient. With zero-, one-, and few-shot single-category learning, the model identifies hate speech one category at a time. With few-shot mixed-category learning, the categories are mixed, and the model is asked to classify an input as sexist, racist, or neither. Zero-shot learning means an example is not provided in the prompt. One-shot learning means that one example is provided, and few-shot means that two or more examples are provided.

@@

@@

The overall results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot-summary), and Appendix \@ref(appendixbzeroshot) provides additional detail. The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category. The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, but the F1 score for each type of hate speech is roughly the same. The overall ratio of matches and mismatches is 75:45. In other words, the accuracy in identifying hate speech in the zero-shot setting is 63 per cent. The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent.

```{r zeroshot-summary, message = FALSE}
# Set-up data for zero-shot racism
zero_shot_result <-
  read_csv(here::here("outputs/data/zero_shot_results.csv"),
           show_col_types = FALSE)

zero_shot_result_racism <-
  zero_shot_result %>%
  filter(temperature == 0 & category == "racist") %>%
  select(category, label, answer, temperature) %>%
  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
  count(label_yn, answer_yn) %>%
  pivot_wider(names_from = answer_yn,
              values_from = n,
              values_fill = 0) %>%
  mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                              label_yn == "Y" ~ "Racist")) %>%
  rename(
    "Actual classification" = label_yn,
    "Not racist" = N,
    "Racist" = Y
  )

@@

# Set-up data for sexism
zero_shot_result_sexism <-
  zero_shot_result %>%
  filter(temperature == 0 & category == "sexist") %>%
  select(category, label, answer, temperature) %>%
  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
  count(label_yn, answer_yn) %>%
  pivot_wider(names_from = answer_yn,
              values_from = n,
              values_fill = 0) %>%
  mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                              label_yn == "Y" ~ "Sexist")) %>%
  rename(
    "Actual classification" = label_yn,
    "Not sexist" = N,
    "Sexist" = Y
  )

zero_shot_result_sexism <-
  zero_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]

# Set-up data for hate speech
zero_shot_result_hate <-
  zero_shot_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer, temperature) %>%
  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
  count(label_yn, answer_yn) %>%
  pivot_wider(names_from = answer_yn,
              values_from = n,
              values_fill = 0) %>%
  mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                              label_yn == "Y" ~ "Hate speech")) %>%
  rename(
    "Actual classification" = label_yn,
    "Not hate speech" = N,
    "Hate speech" = Y
  )

zero_shot_result_hate <-
  zero_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]

# Pull it all together
tp_r <- zero_shot_result_racism[2, 3] %>% as.numeric()
tn_r <- zero_shot_result_racism[1, 2] %>% as.numeric()
fp_r <- zero_shot_result_racism[1, 3] %>% as.numeric()
fn_r <- zero_shot_result_racism[2, 2] %>% as.numeric()

tp_s <- zero_shot_result_sexism[2, 3] %>% as.numeric()
tn_s <- zero_shot_result_sexism[1, 2] %>% as.numeric()
fp_s <- zero_shot_result_sexism[1, 3] %>% as.numeric()
fn_s <- zero_shot_result_sexism[2, 2] %>% as.numeric()

tp_h <- zero_shot_result_hate[2, 3] %>% as.numeric()
tn_h <- zero_shot_result_hate[1, 2] %>% as.numeric()
fp_h <- zero_shot_result_hate[1, 3] %>% as.numeric()
fn_h <- zero_shot_result_hate[2, 2] %>% as.numeric()

zero_racism_accuracy <-
  ((tp_r + tn_r) / (tp_r + tn_r + fp_r + fn_r)) %>% round(4) * 100
zero_racism_precision <- (tp_r / (tp_r + fp_r)) %>% round(4) * 100
zero_racism_recall <- (tp_r / (tp_r + fn_r)) %>% round(4) * 100
zero_racism_f1 <-
  ((2 * zero_racism_precision * zero_racism_recall) / (zero_racism_precision + zero_racism_recall)
  ) %>% round(2)
zero_racism_all <-
  c(zero_racism_accuracy,
    zero_racism_precision,
    zero_racism_recall,
    zero_racism_f1)

zero_sexism_accuracy <-
  ((tp_s + tn_s) / (tp_s + tn_s + fp_s + fn_s)) %>% round(4) * 100
zero_sexism_precision <- (tp_s / (tp_s + fp_s)) %>% round(4) * 100
zero_sexism_recall <- (tp_s / (tp_s + fn_s)) %>% round(4) * 100
zero_sexism_f1 <-
  ((2 * zero_sexism_precision * zero_sexism_recall) / (zero_sexism_precision + zero_sexism_recall)
  ) %>% round(2)
zero_sexism_all <-
  c(zero_sexism_accuracy,
    zero_sexism_precision,
    zero_sexism_recall,
    zero_sexism_f1)

zero_hate_accuracy <-
  ((tp_h + tn_h) / (tp_h + tn_h + fp_h + fn_h)) %>% round(4) * 100
zero_hate_precision <- (tp_h / (tp_h + fp_h)) %>% round(4) * 100
zero_hate_recall <- (tp_h / (tp_h + fn_h)) %>% round(4) * 100
zero_hate_f1 <-
  ((2 * zero_hate_precision * zero_sexism_recall) / (zero_hate_precision + zero_hate_recall)
  ) %>% round(2)
zero_hate_all <-
  c(zero_hate_accuracy,
    zero_hate_precision,
    zero_hate_recall,
    zero_hate_f1)

zero_shot_summary <-
  tibble(
    Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)),
    Metric = rep(c("Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"), 3),
    Percent = c(zero_racism_all, zero_sexism_all, zero_hate_all)
  ) %>%
  pivot_wider(names_from = Metric, values_from = Percent)

zero_shot_summary %>%
  knitr::kable(caption = "Performance of zero-shot learning in hate speech classification",
               booktabs = TRUE,
               digits = 0
               )
```

@@

```{r oneshot-summary}
# Set-up racism
one_shot_result <-
  read.csv(here::here("outputs/data/one_shot_results.csv"))

one_shot_result_racism <-
  one_shot_result %>%
  filter(temperature == 0 & category == "racist") %>%
  select(category, label, answer, temperature) %>%
  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
  count(label_yn, answer_yn) %>%
  pivot_wider(names_from = answer_yn,
              values_from = n,
              values_fill = 0) %>%
  mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                              label_yn == "Y" ~ "Racist")) %>%
  rename(
    "Actual classification" = label_yn,
    "Not racist" = N,
    "Racist" = Y
  )

one_shot_result_racism <-
  one_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]

# Set-up sexism
one_shot_result_sexism <-
  one_shot_result %>%
  filter(temperature == 0 & category == "sexist") %>%
  select(category, label, answer, temperature) %>%
  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
  count(label_yn, answer_yn) %>%
  pivot_wider(names_from = answer_yn,
              values_from = n,
              values_fill = 0) %>%
  mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                              label_yn == "Y" ~ "Sexist")) %>%
  rename(
    "Actual classification" = label_yn,
    "Not sexist" = N,
    "Sexist" = Y
  )

one_shot_result_sexism <-
  one_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]

# Set-up hate
one_shot_result_hate <-
  one_shot_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer, temperature) %>%
  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
  count(label_yn, answer_yn) %>%
  pivot_wider(names_from = answer_yn,
              values_from = n,
              values_fill = 0) %>%
  mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                              label_yn == "Y" ~ "Hate speech")) %>%
  rename(
    "Actual classification" = label_yn,
    "Not hate speech" = N,
    "Hate speech" = Y
  )

one_shot_result_hate <-
  one_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]

# Put it all together
tp_r <- one_shot_result_racism[2, 3] %>% as.numeric()
tn_r <- one_shot_result_racism[1, 2] %>% as.numeric()
fp_r <- one_shot_result_racism[1, 3] %>% as.numeric()
fn_r <- one_shot_result_racism[2, 2] %>% as.numeric()

tp_s <- one_shot_result_sexism[2, 3] %>% as.numeric()
tn_s <- one_shot_result_sexism[1, 2] %>% as.numeric()
fp_s <- one_shot_result_sexism[1, 3] %>% as.numeric()
fn_s <- one_shot_result_sexism[2, 2] %>% as.numeric()

tp_h <- one_shot_result_hate[2, 3] %>% as.numeric()
tn_h <- one_shot_result_hate[1, 2] %>% as.numeric()
fp_h <- one_shot_result_hate[1, 3] %>% as.numeric()
fn_h <- one_shot_result_hate[2, 2] %>% as.numeric()

one_racism_accuracy <-
  ((tp_r + tn_r) / (tp_r + tn_r + fp_r + fn_r)) %>% round(4) * 100
one_racism_precision <- (tp_r / (tp_r + fp_r)) %>% round(4) * 100
one_racism_recall <- (tp_r / (tp_r + fn_r)) %>% round(4) * 100
one_racism_f1 <-
  ((2 * one_racism_precision * one_racism_recall) / (one_racism_precision + one_racism_recall)
  ) %>% round(2)
one_racism_all <-
  c(one_racism_accuracy,
    one_racism_precision,
    one_racism_recall,
    one_racism_f1)

one_sexism_accuracy <-
  ((tp_s + tn_s) / (tp_s + tn_s + fp_s + fn_s)) %>% round(4) * 100
one_sexism_precision <- (tp_s / (tp_s + fp_s)) %>% round(4) * 100
one_sexism_recall <- (tp_s / (tp_s + fn_s)) %>% round(4) * 100
one_sexism_f1 <-
  ((2 * one_sexism_precision * one_sexism_recall) / (one_sexism_precision + one_sexism_recall)
  ) %>% round(2)
one_sexism_all <-
  c(one_sexism_accuracy,
    one_sexism_precision,
    one_sexism_recall,
    one_sexism_f1)

one_hate_accuracy <-
  ((tp_h + tn_h) / (tp_h + tn_h + fp_h + fn_h)) %>% round(4) * 100
one_hate_precision <- (tp_h / (tp_h + fp_h)) %>% round(4) * 100
one_hate_recall <- (tp_h / (tp_h + fn_h)) %>% round(4) * 100
one_hate_f1 <-
  ((2 * one_hate_precision * one_sexism_recall) / (one_hate_precision + one_hate_recall)) %>% round(2)
one_hate_all <-
  c(one_hate_accuracy,
    one_hate_precision,
    one_hate_recall,
    one_hate_f1)

one_shot_summary <-
  tibble(
    Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)),
    Metric = rep(c("Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"), 3),
    Percent = c(one_racism_all, one_sexism_all, one_hate_all)
  ) %>%
  pivot_wider(names_from = Metric, values_from = Percent)

one_shot_summary %>%
  knitr::kable(caption = "Performance of one-shot learning in hate speech classification",
               digits = 0,
               booktabs = TRUE)
```

>>>>

We examine the ability of GPT-3 to identify hate speech in zero-shot, one-shot, and few-shot settings. There are a variety of parameters, such as temperature, that control the degree of text variation. Temperature is a hyper-parameter between zero and one. Lower temperatures mean that the model places more weight on higher-probability tokens. To explore potential variations in the classifications of comments, the temperature is set to 0.3 in our experiments for the zero- and one-shot settings and not varied. In all few-shot settings, the temperature is set to zero. There are two categories of hate speech that are of interest in this paper. The first targets the race of the recipient, and the other targets the gender of the recipient. With zero-, one-, and few-shot single-category learning, the model identifies hate speech one category at a time. With few-shot mixed-category learning, the categories are mixed, and the model is asked to classify an input as sexist, racist, or neither. Zero-shot learning means an example is not provided in the prompt. One-shot learning means that one example is provided, and few-shot means that two or more examples are provided.

@@

For zero- and one-shot learning, each set of 120 comments was classified 100 times by GPT-3 in order to assess the variability of classifications at a temperature of 0.3. The reported performance metrics for these settings are the arithmetic means of each metric across all 100 iterations with the corresponding standard error. In some cases, the model outputted responses that were neither "yes" nor "no". These were counted as "not applicable" and omitted from analysis. Specific numbers are reported in the following sections.

@@

The overall results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot-summary), and Appendix \@ref(appendixbzeroshot) provides additional detail. Out of 6000 classification for each category, the model has 3231 matches (true positives and negatives) and 2691 mismatches (false positives and negatives) in the sexist category, and 3463 matches and 2504 mismatches in the racist category. In the zero-shot learning setting, the model produced 111 responses that were inadmissible. The model performs more accurately when identifying racist comments, with an average accuracy of 58 per cent (SE = 6.5), compared with identifying sexist comments, with an average accuracy of 55 per cent (SE = 5.2). In contrast, the F1 score for classification of sexist speech is slightly higher on average at 63 per cent (SE = 4.3), compared with an average of 58 per cent (SE = 6.7) for racist speech. The overall ratio of matches and mismatches is 6694:5195. In other words, the average accuracy in identifying hate speech in the zero-shot setting is 56 per cent (SE = 4.6). The model has an average F1 score of 70 per cent (SE = 5.7) in this setting.

```{r zeroshot-summary, message = FALSE}
# Set-up data for zero-shot racism
zero_shot_result <-
  read_csv(here::here("outputs/data/zero_shot_results_multiple.csv"),
           show_col_types = FALSE)

# Add iter variable
zero_shot_result <- zero_shot_result %>%
  mutate(iter = floor(`...1`/120) + 1)

zero_shot_result_racism <-
  zero_shot_result %>%
    filter(category == "racist") %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                                label_yn == "Y" ~ "Racist")) %>%
    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)

@@

zero_shot_result_sexism <- 
    zero_shot_result %>%
    filter(category == "sexist") %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                                label_yn == "Y" ~ "Sexist")) %>%
    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
  zero_shot_result_sexism <- zero_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]

zero_shot_result_hate <- 
    zero_shot_result %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                                label_yn == "Y" ~ "Hate speech")) %>%
    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
zero_shot_result_hate <- zero_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]

accuracy_racism <- rep(NA, nrow(zero_shot_result)/120)
accuracy_sexism <- rep(NA, nrow(zero_shot_result)/120)
accuracy_hate <- rep(NA, nrow(zero_shot_result)/120)
precision_racism <- rep(NA, nrow(zero_shot_result)/120)
precision_sexism <- rep(NA, nrow(zero_shot_result)/120)
precision_hate <- rep(NA, nrow(zero_shot_result)/120)
recall_racism <- rep(NA, nrow(zero_shot_result)/120)
recall_sexism <- rep(NA, nrow(zero_shot_result)/120)
recall_hate <- rep(NA, nrow(zero_shot_result)/120)
f1_racism <- rep(NA, nrow(zero_shot_result)/120)
f1_sexism <- rep(NA, nrow(zero_shot_result)/120)
f1_hate <- rep(NA, nrow(zero_shot_result)/120)

# For each iteration:
for (i in 1:(nrow(zero_shot_result)/120)){
  # Racism table
  zero_racism <- 
    zero_shot_result %>%
    filter(category == "racist" & iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                                label_yn == "Y" ~ "Racist")) %>%
    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
  zero_racism <- zero_racism[, c("Actual classification", "Not racist", "Racist")]

  # Sexism table
  zero_sexism <- 
    zero_shot_result %>%
    filter(category == "sexist" & iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                                label_yn == "Y" ~ "Sexist")) %>%
    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
  zero_sexism <- zero_sexism[, c("Actual classification", "Not sexist", "Sexist")]

  # Hate table
  zero_hate <- 
    zero_shot_result %>%
    filter(iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                                label_yn == "Y" ~ "Hate speech")) %>%
    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
  zero_hate <- zero_hate[, c("Actual classification", "Not hate speech", "Hate speech")]

  # Compute accuracy/precision/recall/f1
  tp_r <- zero_racism[2, 3] %>% as.numeric()
  tn_r <- zero_racism[1, 2] %>% as.numeric()
  fp_r <- zero_racism[1, 3] %>% as.numeric()
  fn_r <- zero_racism[2, 2] %>% as.numeric()

  tp_s <- zero_sexism[2, 3] %>% as.numeric()
  tn_s <- zero_sexism[1, 2] %>% as.numeric()
  fp_s <- zero_sexism[1, 3] %>% as.numeric()
  fn_s <- zero_sexism[2, 2] %>% as.numeric()

  tp_h <- zero_hate[2, 3] %>% as.numeric()
  tn_h <- zero_hate[1, 2] %>% as.numeric()
  fp_h <- zero_hate[1, 3] %>% as.numeric()
  fn_h <- zero_hate[2, 2] %>% as.numeric()

  zero_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
  zero_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
  zero_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
  zero_racism_f1 <- ((2*zero_racism_precision*zero_racism_recall)/(zero_racism_precision + zero_racism_recall)) %>% round(2)

  zero_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
  zero_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
  zero_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
  zero_sexism_f1 <- ((2*zero_sexism_precision*zero_sexism_recall)/(zero_sexism_precision + zero_sexism_recall)) %>% round(2)

  zero_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
  zero_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
  zero_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
  zero_hate_f1 <- ((2*zero_hate_precision*zero_sexism_recall)/(zero_hate_precision + zero_hate_recall)) %>% round(2)

  # Add to vectors
  accuracy_racism[i] <- zero_racism_accuracy
  accuracy_sexism[i] <- zero_sexism_accuracy
  accuracy_hate[i] <- zero_hate_accuracy
  precision_racism[i] <- zero_racism_precision
  precision_sexism[i] <- zero_sexism_precision
  precision_hate[i] <- zero_hate_precision
  recall_racism[i] <- zero_racism_recall
  recall_sexism[i] <- zero_sexism_recall
  recall_hate[i] <- zero_hate_recall
  f1_racism[i] <- zero_racism_f1
  f1_sexism[i] <- zero_sexism_f1
  f1_hate[i] <- zero_hate_f1
}

# Sample distributions of accuracy, precision, recall, and f1
zero_racism_summary <- cbind(iter = 1:length(accuracy_racism),
                             accuracy_racism,
                             precision_racism,
                             recall_racism,
                             f1_racism) %>% 
  as_tibble() %>%
  summarise(name = "Racism",
            calc = "Mean",
            accuracy = mean(accuracy_racism),
            precision = mean(precision_racism),
            recall = mean(recall_racism),
            f1 = mean(f1_racism)) %>%
  rbind(summarise(., name = "Racism",
                    calc = "SE",
                    accuracy = sd(accuracy_racism)/sqrt(n()),
                    precision = sd(precision_racism)/sqrt(n()),
                    recall = sd(recall_racism)/sqrt(n()),
                    f1 = sd(f1_racism)/sqrt(n())))

zero_sexism_summary <- cbind(iter = 1:length(accuracy_sexism),
                             accuracy_sexism,
                             precision_sexism,
                             recall_sexism,
                             f1_sexism) %>% 
  as_tibble() %>%
  summarise(name = "Sexism",
            calc = "Mean",
            accuracy = mean(accuracy_sexism),
            precision = mean(precision_sexism),
            recall = mean(recall_sexism),
            f1 = mean(f1_sexism)) %>%
  rbind(summarise(., name = "Sexism",
                  calc = "SE",
                  accuracy = sd(accuracy_sexism)/sqrt(n()),
                  precision = sd(precision_sexism)/sqrt(n()),
                  recall = sd(recall_sexism)/sqrt(n()),
                  f1 = sd(f1_sexism)/sqrt(n())))

zero_hate_summary <- cbind(iter = 1:length(accuracy_hate),
                             accuracy_hate,
                             precision_hate,
                             recall_hate,
                             f1_hate) %>% 
  as_tibble() %>%
  summarise(name = "Overall",
            calc = "Mean",
            accuracy = mean(accuracy_hate),
            precision = mean(precision_hate),
            recall = mean(recall_hate),
            f1 = mean(f1_hate)) %>%
  rbind(summarise(., name = "Overall",
                  calc = "SE",
                  accuracy = sd(accuracy_hate)/sqrt(n()),
                  precision = sd(precision_hate)/sqrt(n()),
                  recall = sd(recall_hate)/sqrt(n()),
                  f1 = sd(f1_hate)/sqrt(n())))

zero_summary <- rbind(zero_racism_summary, zero_sexism_summary, zero_hate_summary)

zero_summary %>% pivot_longer(cols = !c(name, calc), names_to = "metric") %>%
  pivot_wider(names_from = c(calc), values_from = value) %>%
  mutate(name = case_when(metric == "accuracy" ~ name, TRUE ~ ""),
         metric = str_to_title(metric),
         Mean = round(Mean),
         SE = round(SE, 1)) %>%
  knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
        caption = "Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.",
        booktabs = TRUE,
        linesep = "") %>%
  kableExtra::column_spec(column = 1, bold = TRUE)
```

@@

```{r oneshot-summary}
# Set-up racism
one_shot_result <-
  read.csv(here::here("outputs/data/one_shot_results_multiple.csv"))

# Add iter variable
one_shot_result <- one_shot_result %>%
  mutate(iter = floor(X/120) + 1)

one_shot_result_racism <- 
  one_shot_result %>%
  filter(category == "racist") %>%
  select(category, label, answer, temperature) %>%
  mutate(answer = tolower(answer) %>% trimws(),
         label_yn = ifelse(grepl("not", label), "N", "Y"),
         answer_yn = case_when(str_detect(answer, "no") ~ "N",
                              str_detect(answer, "yes") ~ "Y",
                              TRUE ~ "Other")) %>%
  filter(answer_yn != "Other") %>%
  count(label_yn, answer_yn) %>%
  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
  mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                              label_yn == "Y" ~ "Racist")) %>%
  rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
one_shot_result_racism <- one_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]

# Sexism table
one_shot_result_sexism <- 
  one_shot_result %>%
  filter(category == "sexist") %>%
  select(category, label, answer, temperature) %>%
  mutate(answer = tolower(answer) %>% trimws(),
         label_yn = ifelse(grepl("not", label), "N", "Y"),
         answer_yn = case_when(str_detect(answer, "no") ~ "N",
                              str_detect(answer, "yes") ~ "Y",
                              TRUE ~ "Other")) %>%
  filter(answer_yn != "Other") %>%
  count(label_yn, answer_yn) %>%
  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
  mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                              label_yn == "Y" ~ "Sexist")) %>%
  rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
one_shot_result_sexism <- one_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]

# Hate table
one_shot_result_hate <- 
  one_shot_result %>%
  select(category, label, answer, temperature) %>%
  mutate(answer = tolower(answer) %>% trimws(),
         label_yn = ifelse(grepl("not", label), "N", "Y"),
         answer_yn = case_when(str_detect(answer, "no") ~ "N",
                              str_detect(answer, "yes") ~ "Y",
                              TRUE ~ "Other")) %>%
  filter(answer_yn != "Other") %>%
  count(label_yn, answer_yn) %>%
  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
  mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                              label_yn == "Y" ~ "Hate speech")) %>%
  rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
one_shot_result_hate <- one_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]

accuracy_racism <- rep(NA, nrow(one_shot_result)/120)
accuracy_sexism <- rep(NA, nrow(one_shot_result)/120)
accuracy_hate <- rep(NA, nrow(one_shot_result)/120)
precision_racism <- rep(NA, nrow(one_shot_result)/120)
precision_sexism <- rep(NA, nrow(one_shot_result)/120)
precision_hate <- rep(NA, nrow(one_shot_result)/120)
recall_racism <- rep(NA, nrow(one_shot_result)/120)
recall_sexism <- rep(NA, nrow(one_shot_result)/120)
recall_hate <- rep(NA, nrow(one_shot_result)/120)
f1_racism <- rep(NA, nrow(one_shot_result)/120)
f1_sexism <- rep(NA, nrow(one_shot_result)/120)
f1_hate <- rep(NA, nrow(one_shot_result)/120)

# For each iteration:
for (i in 1:(nrow(one_shot_result)/120)){
  # Racism table
  one_racism <- 
    one_shot_result %>%
    filter(category == "racist" & iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                                label_yn == "Y" ~ "Racist")) %>%
    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
  one_racism <- one_racism[, c("Actual classification", "Not racist", "Racist")]

  # Sexism table
  one_sexism <- 
    one_shot_result %>%
    filter(category == "sexist" & iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                                label_yn == "Y" ~ "Sexist")) %>%
    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
  one_sexism <- one_sexism[, c("Actual classification", "Not sexist", "Sexist")]

  # Hate table
  one_hate <- 
    one_shot_result %>%
    filter(iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                                label_yn == "Y" ~ "Hate speech")) %>%
    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
  one_hate <- one_hate[, c("Actual classification", "Not hate speech", "Hate speech")]

  # Compute accuracy/precision/recall/f1
  tp_r <- one_racism[2, 3] %>% as.numeric()
  tn_r <- one_racism[1, 2] %>% as.numeric()
  fp_r <- one_racism[1, 3] %>% as.numeric()
  fn_r <- one_racism[2, 2] %>% as.numeric()
